### 2008-08-17 doc/a-rex/arex_tech_doc.tex
Conversion from GM to A-REX is done in A-REX document. Language and citations fixes to follow.

\begin{itemize}
\item \textit{subject} - user certificate's subject, also known as the distinguished
name (DN)
\item \textit{starttime} - GMT time when the job was accepted represented
in the Generalized Time format of LDAP 
\item \textit{lifetime} - time period to preserve the SD after the job has
finished in seconds
\item \textit{cleanuptime} - GMT time when the job should be removed from
the cluster and it's SD deleted in Generalized Time format
\item \textit{notify} - email addresses and flags to send mail to about
the job specified status changes
\item \textit{processtime} - GMT time when to start processing the job in
Generalized Time format
\item \textit{exectime} - GMT time when to start job execution in Generalized
Time format
\item \textit{expiretime} - GMT time when the credentials delegated to the
job expire in Generalized Time format
\item \textit{rerun} - number of retries left to rerun the job
\item \textit{jobname} - name of the job as supplied by the user
\item \textit{lrms} - name of the LRMS backend to be used for local submission
\item \textit{queue} - name of the queue to run the job at
\item \textit{localid} - job id in LRMS (appears only after the job has
reached state \textbf{InLRMS})
\item \textit{args} - executable name followed by a list of command-line
arguments
\item \textit{downloads} - number of files to download into the SD before
execution
\item \textit{uploads} - number of files to upload from the SD after execution
\item \textit{gmlog} - directory name which holds files containing information
about the job when accessed through GridFTP interface
\item \textit{clientname} - name (as provided by the user interface) and
ip address:port of the submitting client machine
\item \textit{clientsoftware} - version of software used to submit the job
\item \textit{sessiondir} - the job's SD
\item \textit{failedstate} - state in which job failed (available only if
it is possible to restart the job)
\item \textit{jobreport} - URL of a user requested \emph{logger service}.
The GM will also send job records to this service in addition to the
default logger service configured in the configuration (This feature
does not work in current implementation).
\end{itemize}
\end{itemize}
This file is filled partially during job submission and fully when
the job moves from the \textbf{Accepted} to the \textbf{Preparing}
state.

@@

A-REX introduces a new operation in addition to those provided by
BES. It does that by defining its own port-type with the single operation
\emph{ChangeActivityStatus} (see Appendix D). This operation provides
a way to request simple transfers between states of jobs and corresponding
actions.

@@

The A-REX also supportd the Delegation Interface (see Appendix E).
This is a common purpose interface to be used by ARC services which
accepts delegated credentials from clients. The Delegation Interface
implements two operations: initiatialization of credentials delegation
(DelegateCredentialsInit) and update/renewal of credentials (UpdateCredentials).

@@

A-REX accepts JSDL documents having the following additional elements
(see Appendix F):

@@

\begin{itemize}
\item \textit{libarex.so} - The main module providing main functionality
and web interface. It is implemented as HTTP and SOAP service inside
HED. It is responsible for processing jobs, moving them through states
and running other modules.
\item \textit{downloader} - This is a module responsible for gathering input
files in the SD. It processes the \textit{job.ID.input} file and updates
it.
\item \textit{uploader} - This module is responsible for delivering output
files to the specified SEs and registration at an Indexding Service
(like RLS) as needed. It processes and updates the \textit{job.ID.output}
file.
\item \emph{cache-register} - Utility to register cached data into an Indexing
Service. It reads and modifies cache informational files \emph{old}
and \emph{new} (as described in section \ref{sec:cache}). Configuration
is read directly from the GM's configuration file (see section \ref{SubSection: ConfigFile}).
It is run by the GM every 5 minutes.
\item \emph{frontend-info-collector} - Utility to gather information about
the frontend. It puts collected information into the \emph{job.ID.diag}
file.
\item \emph{gm-kick} - Sends a signal to the A-REX though a FIFO file to
wake it up. It's used to increase responsiveness of A-REX.
\item \emph{cluster+qju.pl} - Collects and generates information about computing
resource as XML document in NoruGrid and Glue 2 format.
\end{itemize}
The following modules are always run under the Unix account to which
a Grid user is mapped.

@@

\begin{lyxlist}{00.00.0000}
\item [{new}] - new job, new credentials
\item [{renew}] - old job, new credentials
\item [{write}] - write/delete file, create/delete directory (through gridftp)
\item [{read}] - read file, directory, etc. (through gridftp)
\item [{extern}] - call external program (grid-manager)
\end{lyxlist}
\end{lyxlist}

@@

Authorization is performed by generic means provided by HED framework.
Currently A-REX does not implement any internal authorization tecniques.

@@

The GM comes with support for several LRMS. And this number is slowly
growing. Features explained below are for \textbf{PBS/Torque} backend.
This support is provided through \textit{submit-pbs-job}, \textit{cancel-pbs-job},
\textit{scan-pbs-job} scripts. \textit{submit-pbs-job} creates job's
script and submits it to PBS. Created job's script is responsible
for moving data between frontend machine and cluster node (if required)
and execution of actual job. Alternatively it can download input files
and upload output if \emph{{}``localtransfer no''} is specified
in the configuration file.

Behavior of submission script is mostly controlled using environment
variables. Most of them can be specified on frontend in GM's environment
and overwritten on cluster's node through PBS configuration. Some
of them may be set in configuration file too.

\textbf{\textit{PBS\_BIN\_PATH}} - path to PBS executables. Like \emph{/usr/local/bin}
for example. \emph{pbs\_bin\_path} configuration command.

\textbf{\textit{PBS\_LOG\_PATH}} - path to PBS server logs. \emph{pbs\_log\_path}
configuration command.

\textbf{\textit{TMP\_DIR}} - path to directory to store temporary
files. Default value is \emph{/tmp}. \emph{tmpdir} configuration command.

\textbf{\textit{RUNTIME\_CONFIG\_DIR}} - path where runtime setup
scripts can be found. \emph{runtimedir} configuration command.

\textbf{\textit{GNU\_TIME}} - path to GNU time utility. It is important
to path to utility compatible with GNU time. If such utility is not
available, modify \textit{submit-pbs-job} to either reset this variable
or change usage of available utility. \emph{gnu\_time} configuration
command.

\textbf{\textit{NODENAME}} - command to obtain name of cluster's node.
Default is \emph{/bin/hostname -f}. \emph{nodename} configuration
command.

@@

\textbf{\textit{RUNTIME\_FRONTEND\_SEES\_NODE}} - if defined should
contain path corresponding to \textit{RUNTIME\_LOCAL\_SCRATCH\_DIR}
as seen on \textbf{frontend} machine. \emph{shared\_scratch} configuration
command.

\textbf{\textit{RUNTIME\_NODE\_SEES\_FRONTEND}} - if set to {}``\emph{no}''
means computing node does not share filesystem with frontend. In that
case content of the SD is moved to computing node by using means provided
by the LRMS. Results are moved back after job's execution in a same
way. \emph{shared\_filesystem} configuration command.

Figures \ref{fig:no node scratch},\ref{fig:node scratch, not vis on front},\ref{fig:node scratch, vis on front}
present some possible combinations for RUNTIME\_LOCAL\_SCRATCH\_DIR
and RUNTIME\_FRONTEND\_SEES\_NODE and explain how data movement is
performed. Pictures a) corresponds to the situation right after all
input files have been gathered in the session directory and show the
actions taken right after the job's script starts. Pictures b) shows
the situation while the job is running and the actions which are taken
right after it has finished. Pictures c) illustrates the final situation,
when the job's output files are ready to be uploaded to an external
storage element or be downloaded by the user.

@@

\caption{\label{fig:no node scratch}Both RUNTIME\_LOCAL\_SCRATCH\_DIR and
RUNTIME\_FRONTEND\_SEES\_NODE are undefined. It is assumed that session
directories are visible from computing nodes. The job is executed
directly in the session directory prepared by GM on the frontend.}
\end{figure}
%
\begin{figure}[htbp]
\begin{centering}
\includegraphics{pic3}
\par\end{centering}

@@

\subsection{Setup of the Grid Manager}

For in-depth information about how to properly setup the GM and related
software please read {}``NorduGrid ARC server installation instructions''
at \url{http://www.nordugrid.org/documents/ng-server-install.html}.
Follow that manual to install GM, configure and run it. Additional
tips are described here.

The GM is designed to be able to run both as root and as ordinary
user. You can chose the name of the user by using corresponding command
in configuration file. It is better run GM as root if You want to
serve few users.

The GM writes debug information into a file /var/log/grid-manager.log
by default. . Also file /var/log/gm-jobs.log (default path in configuration
template, turned off by default) contains information about all started
and finished jobs, 2 lines per job (1 when job is started and 1 after
it finished).

@@

Refer to the description of the \emph{User Interface} part \cite{ui}
and extensions to RSL \cite{xrsl} for using the GM.

@@

Bot GM and GFS are primarily designed to be run by the \emph{root}
UNIX account and serve multiple global Grid identities mapped to several
UNIX accounts. Nevertheless it is possible to use \emph{non-root}
accounts to run these services at the cost of some functionality loss
as described below.

There are no drawbacks of running GFS with \emph{gaclplugin} or \emph{fileplugin}
under a \emph{non-root} account as long as the only Grid identity
used is that of the user who runs the services and all served files
and directories are owned by the server's account.

In order for GM and GFS with \emph{jobplugin} to be able to cooperate,
both services must be run either by the same non-root account or one
of the services must be run under the \emph{root} account. This is
needed because the two services communicate over a local filesystem,
hence they must have \emph{full} access to the same set of files.

As long as GFS with \emph{jobplugin} is run under a non-root account,
no mapping from Grid identity to local UNIX account takes place. All
alowed Grid users are assigned the server's account and are then processes
by GM using same account. The only way to overcome this limitation
is to run one GFS per local account with proper access control configured.

Because GM has to impersonate a user's local account while communicating
with the LRMS, it can serve only the account it is run under (unless
it is run under the \emph{root} account, of course). As in the case
of GFS, multiple instances of GM may be run, one per local account.
This solution has some drawbacks. The GM looses possibility to share
cached files among serviced users. In addition, it is not possible
to control the load on a frontend by limiting the number of simultatenuosly
running \emph{downloader} and \emph{uploader} modules.

One also has to take into account that the private part of the GSI
infrastructure (private key of a host at least) has to be duplicated
for every account used to run GFS.

@@

\subsection*{Virtual tree}

Under the mount point of the jobplugin, a user connecting with a gridftp
client will see virtual directories representing the jobs belonging
to him/her. Directory names are job identifiers, each representing
one job. These directories are directly connected to session directories
of jobs and contain the files and subdirectories that are visible
on the frontend.

If a job's xRSL has \emph{gmlog} specified, then the job's directory
also contains a virtual subdirectory of that name holding files with
information about the job as created by GM. The 'errors' and 'status'
files are especially usefull for troubleshooting. 'errors' contains
the stderr output of the various modules run by GM during job processing
stages (downloader, uploader, job's submission to LRMS). 'status'
contains one word representing the job's state.

Also under the jobplugin's mount point there is an additional directory
named \char`\"{}new\char`\"{} -- used to submit new jobs -- and another
directory named ''info''. The latter has subdirectories named after
job ids, each of which contains files with information about a job.
These are the same files that can be accessed in the subdirectory
specified through \emph{gmlog}.

\subsection*{Submission}

Each xRSL put into the {}``new'' directory by a gridftp client is
treated as a new job's description. GFS's jobplugin parses the xRSL
and returns the client a positive response if there were no errors
in the request.

The new job gets an identifier and a directory with the corresponding
name appears. If the job's description contains input files which
should be transferred from the client's machine, the client must upload
them to that directory under specified names.

The job identifier reserved by GFS to a new job must be somehow communicated
back to the client. Within the bounds of the FTP protocol, this is
achieved in the following way. Prior to uploading the xRSL, the client
issues a CWD command to change the current directory to {}``new''.
In turn, the server responds with a redirect to the new session directory
named after the reserved identifier. The client has now found out
the job's id, and proceeds with uploading the xRLS.

\subsection*{Actions}

Various actions to affect processing of an existing job are requested
by uploading special xRSL files into directory {}``new''. Such an
xRSL may consist of only 2 parameters - \emph{action} for action to
be performed, and \emph{jobid} to identify the job to be affected.
All other parameters are ignored.

The currently supported actions are:

\begin{lyxlist}{00.00.0000}
\item [{\emph{cancel}}] to cancel a job
\item [{\emph{clean}}] to remove a job from computing resource
\item [{\emph{renew}}] to renew credentials delegated to a job
\item [{\emph{restart}}] to restart a job after failure at some phases
\end{lyxlist}
Alternatively, it is also possible to perform some of these actions
by using the shortcut FTP operations described below.

\subsubsection*{Cancel}

A job is canceled by performing a DELE (delete file) command on the
directory representing the job. It can take some time (a few minutes)
before the job is actually canceled. Nevertheless, the client gets
a response immediately.

\subsubsection*{Clean}

A job's content is cleaned by performing a RMD (remove directory)
command on the directory representing the job. If the job is in \char`\"{}FINISHED\char`\"{}
state it will be cleaned immediately. Otherwise it will be cleaned
after it reaches state \char`\"{}FINISHED\char`\"{}.

\subsubsection*{Renew}

If a client requests CWD to a job's session directory, credentials
passed during authentication are compared to the current credentials
of the job. If the validity time of the new credentials is longer,
the job's current credentials are replaced with the new ones.

\section*{Appendix C. Configuration schema of A-REX}

@@

\section*{Appendix C. Error messages of A-REX}

\begin{tabular}{|p{2.5in}|p{4in}|}
\hline 
\emph{Error string}&
\emph{Reason/description}\tabularnewline
\hline 
Internal error&
Error in internal algorithm\tabularnewline
\hline 
Internal error: can't read local file&
Error manipulating files in the control directory\tabularnewline
\hline 
Failed reading local job information&
-//-\tabularnewline
\hline 
Failed reading status of the job&
-//-\tabularnewline
\hline 
Failed writing job status&
-//-\tabularnewline
\hline 
Failed during processing failure&
-//-\tabularnewline
\hline 
Serious troubles (problems during processing problems)&
-//-\tabularnewline
\hline 
Failed initiating job submission to LRMS&
Could not run backend executable to pass job to LRMS\tabularnewline
\hline 
Job submission to LRMS failed&
Backend executable supposed to pass job to LRMs returned non-zero
exit code\tabularnewline
\hline 
Failed extracting LRMS ID due to some internal error&
Output of Backend executable supposed to contain local ID of passed
job could not be parsed\tabularnewline
\hline 
Failed in files upload (post-processing)&
Failed to upload some or all output files\tabularnewline
\hline 
Failed in files upload due to expired credentials - try to renew&
Failed to upload some or all output files most probably due to expired
credentials (proxy certificate)\tabularnewline
\hline 
Failed to run uploader (post-processing)&
Could not run \emph{uploader} executable\tabularnewline
\hline 
uploader failed (postprocessing)&
Generic error related to \emph{uploader} component\tabularnewline
\hline 
Failed in files download (pre-processing)&
Failed to upload some or all input files\tabularnewline
\hline 
Failed in files download due to expired credentials - try to renew&
Failed to download some or all input files most probably due to expired
credentials (proxy certificate)\tabularnewline
\hline 
Failed to run downloader (pre-processing)&
Could not run \emph{downloader} executable\tabularnewline
\hline
downloader failed (preprocessing)&
Generic error related to \emph{downloader} component\tabularnewline
\hline
User requested to cancel the job&
GM detected external request to cancel this job, most probably issued
by user\tabularnewline
\hline
Could not process RSL&
Job description could not be processed to syntax errors or missing
elements\tabularnewline
\hline
User requested dryrun. Job skiped.&
Job description contains request not to process this job\tabularnewline
\hline
LRMS error: (CODE) DESCRIPTION&
LRMS returned error. CODE is replaced with numeric code of LRMS, and
DESCRIPTION with textual description\tabularnewline
\hline
Plugin at state STATE failed: OUTPUT&
External plugin specified in GM's configuration returned non-zero
exit code. STATE is replcaced by name of state to which job was going
to be passed, OUTPUT by textual output generated by plugin.\tabularnewline
\hline
Failed running plugin at state STATE&
External plugin specified in GM's configuration could not be executed.\tabularnewline
\hline
\end{tabular}

\begin{tabular}{|p{2.5in}|p{4in}|}
\hline 
\emph{Error string}&
\emph{Reason/description}\tabularnewline
\hline 
Internal error in downloader&
Generic error \tabularnewline
\hline 
Input file: URL - unknown error&
Generic error \tabularnewline
\hline 
Input file: URL - unexpected error&
Generic error \tabularnewline
\hline 
Input file: URL - bad source URL&
Source URL is either malformed or not supported\tabularnewline
\hline 
Input file: URL - bad destination URL&
Shouldn't happen\tabularnewline
\hline 
Input file: URL - failed to resolve source locations&
File either not registred or other problems related to Data Indexing
service.\tabularnewline
\hline 
Input file: URL - failed to resolve destination locations&
Shouldn't happen\tabularnewline
\hline 
Input file: URL - failed to register new destination file&
Shouldn't happen\tabularnewline
\hline 
Input file: URL - can't start reading from source&
Problems related to accessing instance of file at Data Storing service.\tabularnewline
\hline 
Input file: URL - can't read from source&
-//-\tabularnewline
\hline 
Input file: URL - can't start writing to destination&
Access problems in a session directory\tabularnewline
\hline 
Input file: URL - can't write to destination&
-//-\tabularnewline
\hline 
Input file: URL - data transfer was too slow&
Timeouted while trying to download file\tabularnewline
\hline 
Input file: URL - failed while closing connection to source&
Shouldn't happen\tabularnewline
\hline 
Input file: URL - failed while closing connection to destination&
Shouldn't happen\tabularnewline
\hline 
Input file: URL - failed to register new location&
Shouldn't happen\tabularnewline
\hline 
Input file: URL - can't use local cache&
Problems with GM cache \tabularnewline
\hline 
Input file: URL - system error&
Operating System returned error code where unexpected\tabularnewline
\hline 
Input file: URL - delegated credentials expired&
Access to source requires credententials and they are either outdated
or missing (not delegated).\tabularnewline
\hline 
User file: FILENAME - Bad information about file: checksum can't be
parsed.&
In job description there is a checksum provided for file uploadable
by user interface and this record can't be interpreted.\tabularnewline
\hline 
User file: FILENAME - Bad information about file: size can't be parsed.&
In job description there is a size provided for file uploadable by
user interface and this record can't be interpreted.\tabularnewline
\hline 
User file: FILENAME - Expected file. Directory found.&
Instead of file uploadable by user interface GM found directory with
same name in a session directory.\tabularnewline
\hline 
User file: FILENAME - Expected ordinary file. Special object found.&
Instead of file uploadable by user interface GM found special object
with same name in a session directory.\tabularnewline
\hline 
User file: FILENAME - Delivered file is bigger than specified.&
The size of file uploadable by user interface is bigger than specified
in job description.\tabularnewline
\hline
User file: FILENAME - Delivered file is unreadable.&
GM can't check user uploadable file due to some internal error. Most
probably due to improperly configured local permissions.\tabularnewline
\hline
User file: FILENAME - Could not read file to compute checksum.&
GM can't read user uploadable file due to some internal error. Most
probably due to improperly configured local permissions.\tabularnewline
\hline
User file: FILENAME - Timeout waiting&
GM waited for user uploadable file too long.\tabularnewline
\hline
\end{tabular}

\begin{lyxcode}
~
\end{lyxcode}

\section*{Appendix D. A-REX WSDL}

@@

\section*{Appendix E. Delegation WSDL}

@@

\section*{Appendix F. ARC extensions for JSDL schema}

@@

</xsd:schema>

>>>>

\begin{itemize}
\item \textit{subject} - user certificate's subject, also known as the distinguished
name (DN)
\item \textit{starttime} - GMT time when the job was accepted represented
in the Generalized Time format of LDAP 
\item \textit{lifetime} - time period to preserve the SD after the job has
finished in seconds
\item \textit{cleanuptime} - GMT time when the job should be removed from
the cluster and it's SD deleted in Generalized Time format
\item \textit{notify} - email addresses and flags to send mail to about
the job specified status changes
\item \textit{processtime} - GMT time when to start processing the job in
Generalized Time format
\item \textit{exectime} - GMT time when to start job execution in Generalized
Time format
\item \textit{expiretime} - GMT time when the credentials delegated to the
job expire in Generalized Time format
\item \textit{rerun} - number of retries left to rerun the job
\item \textit{jobname} - name of the job as supplied by the user
\item \textit{lrms} - name of the LRMS backend to be used for local submission
\item \textit{queue} - name of the queue to run the job at
\item \textit{localid} - job id in LRMS (appears only after the job has
reached state \textbf{InLRMS})
\item \textit{args} - executable name followed by a list of command-line
arguments
\item \textit{downloads} - number of files to download into the SD before
execution
\item \textit{uploads} - number of files to upload from the SD after execution
\item \textit{gmlog} - directory name which holds files containing information
about the job when accessed through GridFTP interface
\item \textit{clientname} - name (as provided by the user interface) and
ip address:port of the submitting client machine
\item \textit{clientsoftware} - version of software used to submit the job
\item \textit{sessiondir} - the job's SD
\item \textit{failedstate} - state in which job failed (available only if
it is possible to restart the job)
\item \textit{jobreport} - URL of a user requested \emph{logger service}.
The A-REX will also send job records to this service in addition to
the default logger service configured in the configuration (This feature
does not work in current implementation).
\end{itemize}
\end{itemize}
This file is filled partially during job submission and fully when
the job moves from the \textbf{Accepted} to the \textbf{Preparing}
state.

@@

A-REX introduces a new operation in addition to those provided by
BES. It does that by defining its own port-type with the single operation
\emph{ChangeActivityStatus} (see Appendix C). This operation provides
a way to request simple transfers between states of jobs and corresponding
actions.

@@

The A-REX also supportd the Delegation Interface (see Appendix D).
This is a common purpose interface to be used by ARC services which
accepts delegated credentials from clients. The Delegation Interface
implements two operations: initiatialization of credentials delegation
(DelegateCredentialsInit) and update/renewal of credentials (UpdateCredentials).

@@

A-REX accepts JSDL documents having the following additional elements
(see Appendix E):

@@

\begin{itemize}
\item \textit{libarex.so} - The main module providing main functionality
and web interface. It is implemented as HTTP and SOAP service inside
HED. It is responsible for processing jobs, moving them through states
and running other modules.
\item \textit{downloader} - This is a module responsible for gathering input
files in the SD. It processes the \textit{job.ID.input} file and updates
it.
\item \textit{uploader} - This module is responsible for delivering output
files to the specified SEs and registration at an Indexding Service
(like RLS) as needed. It processes and updates the \textit{job.ID.output}
file.
\item \emph{cache-register} - Utility to register cached data into an Indexing
Service. It reads and modifies cache informational files \emph{old}
and \emph{new} (as described in section \ref{sec:cache}). Configuration
is read directly from the A-REX's configuration file (see section
\ref{SubSection: ConfigFile}). It is run by the A-REX every 5 minutes.
\item \emph{frontend-info-collector} - Utility to gather information about
the frontend. It puts collected information into the \emph{job.ID.diag}
file.
\item \emph{gm-kick} - Sends a signal to the A-REX though a FIFO file to
wake it up. It's used to increase responsiveness of A-REX.
\item \emph{cluster+qju.pl} - Collects and generates information about computing
resource as XML document in NoruGrid and Glue 2 format.
\end{itemize}
The following modules are always run under the Unix account to which
a Grid user is mapped.

@@

\begin{lyxlist}{00.00.0000}
\item [{new}] - new job, new credentials
\item [{renew}] - old job, new credentials
\item [{write}] - write/delete file, create/delete directory
\item [{read}] - read file, directory, etc.
\item [{extern}] - call external program 
\end{lyxlist}
\end{lyxlist}

@@

Authorization is performed by generic means provided by HED framework.
Currently A-REX does not implement any internal authorization tecniques
except those imposed by Access Policy assigned to jobs through AccessControl
element of assigned JSDL.

@@

The A-REX comes with support for several LRMS. And this number is
slowly growing. Features explained below are for \textbf{PBS/Torque}
backend. This support is provided through \textit{submit-pbs-job},
\textit{cancel-pbs-job}, \textit{scan-pbs-job} scripts. \textit{submit-pbs-job}
creates job's script and submits it to PBS. Created job's script is
responsible for moving data between frontend machine and cluster node
(if required) and execution of actual job. Alternatively it can download
input files and upload output if \emph{{}``localtransfer=no''} is
specified in the configuration file.

Behavior of submission script is mostly controlled using environment
variables. Most of them can be specified on frontend in A-REX's environment
and overwritten on cluster's node through PBS configuration. Some
of them may be set in configuration file too.

\textbf{\textit{PBS\_BIN\_PATH}} - path to PBS executables. Like \emph{/usr/local/bin}
for example. \emph{}Corresponds to \emph{pbs\_bin\_path} configuration
command.

\textbf{\textit{PBS\_LOG\_PATH}} - path to PBS server logs. Corresponds
to \emph{pbs\_log\_path} configuration command.

\textbf{\textit{TMP\_DIR}} - path to directory to store temporary
files. Default value is \emph{/tmp}. Corresponds to \emph{tmpdir}
configuration command.

\textbf{\textit{RUNTIME\_CONFIG\_DIR}} - path where runtime setup
scripts can be found. Corresponds to \emph{runtimedir} configuration
command.

\textbf{\textit{GNU\_TIME}} - path to GNU time utility. It is important
to provide path to utility compatible with GNU time. If such utility
is not available, modify \textit{submit-pbs-job} to either reset this
variable or change usage of available utility. Corresponds to \emph{gnu\_time}
configuration command.

\textbf{\textit{NODENAME}} - command to obtain name of cluster's node.
Default is \emph{/bin/hostname -f}. Corresponds to \emph{nodename}
configuration command.

@@

\textbf{\textit{RUNTIME\_FRONTEND\_SEES\_NODE}} - if defined should
contain path corresponding to \textit{RUNTIME\_LOCAL\_SCRATCH\_DIR}
as seen on \textbf{frontend} machine. Corresponds to \emph{shared\_scratch}
configuration command.

\textbf{\textit{RUNTIME\_NODE\_SEES\_FRONTEND}} - if set to {}``\emph{no}''
means computing node does not share filesystem with frontend. In that
case content of the SD is moved to computing node by using means provided
by the LRMS. Results are moved back after job's execution in a same
way. Corresponds to \emph{shared\_filesystem} configuration command.

Figures \ref{fig:no node scratch},\ref{fig:node scratch, not vis on front},\ref{fig:node scratch, vis on front}
present some possible combinations for RUNTIME\_LOCAL\_SCRATCH\_DIR
and RUNTIME\_FRONTEND\_SEES\_NODE and explain how data movement is
performed. Pictures a) correspond to the situation right after all
input files have been gathered in the session directory and show the
actions taken right after the job's script starts. Pictures b) show
the situation while the job is running and the actions which are taken
right after it has finished. Pictures c) illustrate the final situation,
when the job's output files are ready to be uploaded to an external
storage element or be downloaded by the user.

@@

\caption{\label{fig:no node scratch}Both RUNTIME\_LOCAL\_SCRATCH\_DIR and
RUNTIME\_FRONTEND\_SEES\_NODE are undefined. It is assumed that session
directories are visible from computing nodes. The job is executed
directly in the session directory prepared by the A-REX on the frontend.}
\end{figure}
%
\begin{figure}[htbp]
\begin{centering}
\includegraphics{pic3}
\par\end{centering}

@@

\subsection{Setup of the A-REX}

The A-REX service is a plugable module of the HED. Si first You need
to setup your HED - see HED documentation.

Then You need to add A-REX to the HED configuration. Add new <Name>
element inside <Plugins> containing string \emph{arex}. That will
make HED load libarex plugin library. Then add new <Service> element
with attribute name=''a-rex''. That will instantiate A-REX service.
Now to make service accessible extend <Plexer> element with new <next>
refering to service's id. Write <Service> element carefully - here
is an example:

\begin{lyxcode}
~~~~<!-{}-~A-Rex~service~-{}->

~~~~<Service~name=\char`\"{}a-rex\char`\"{}~id=\char`\"{}a-rex\char`\"{}>

~~~~~~<!-{}-~Optional~endpoint~element~is~advised~in~case~of~multiple~IP~adresses~-{}->

~~~~~~<arex:endpoint>https://localhost:60000/arex</arex:endpoint>

~~~~~~<!-{}-~Use~information~generated~by~identity.map~plugin~or~default~provided~below~-{}->

~~~~~~<arex:usermap><arex:defaultLocalName>nobody</arex:defaultLocalName></arex:usermap>

~~~~~~<!-{}-~grid-manager~part~of~a-rex~requires~legacy~configuration~file.

~~~~~~~~~~~Use~arc\_arex.conf~example~or~write~own.~-{}->

~~~~~~<arex:gmconfig>/etc/arc\_arex.conf</arex:gmconfig>

~~~~</Service>
\end{lyxcode}
For in-depth information about available elements see Appendix B.

Use a template arc\_arex.conf or write own A-REX configuration file.
For information about format and available configuration commands
see Section \ref{SubSection: ConfigFile}.

@@

Please read \emph{User Manual {[}]} for usage instructions.

@@

The A-REX is primarily designed to be run by the \emph{root} UNIX
account and serve multiple global Grid identities mapped to several
UNIX accounts. Nevertheless it is possible to use \emph{non-root}
accounts to run that service at the cost of some functionality loss
as described below.

There are no drawbacks of running A-REX under a \emph{non-root} account
as long as the only UNIX identity used is that of the user who runs
the services and all served files and directories are owned by the
server's account. Because A-REX has to impersonate a user's local
account while communicating with the LRMS, it can serve only the account
it is run under (unless it is run under the \emph{root} account, of
course).

@@

In addition to the BES interface A-REX provides access to the SD through
pure HTTP(S) interface. This functionality is used for uploading user-stageable
files during job submission and for staging out result files produced
by job. It can also be used to monitor job execution by checking content
of application dependant files in SD.

The BES defines job identifier as WS Addressing {[}] Endpoint Reference
(EPR) - XML document. The EPR is extendable and the A-REX adds it
own element JobSessionDir belonging to namespace http://www.nordugrid.org/schemas/a-rex
as direct child of ReferenceParameters element. This new element contains
the URL of SD.

Obtained URL shoud be extended with file names relative to SD and
HTTP methods PUT and GET may be used to upload/download content of
those files. For directories - including SD itself - GET method is
supported shich returns HTML encoded non-recursive list of files and
firectories. The files and subdirectories have their URLs inside HTML
element <A>.

\section*{Appendix B. Configuration schema of A-REX}

@@

\section*{Appendix C. A-REX WSDL}

@@

\section*{Appendix D. Delegation WSDL}

@@

\section*{Appendix E. ARC extensions for JSDL schema}

@@

\section*{Appendix F. Error messages of A-REX}

\begin{tabular}{|p{2.5in}|p{4in}|}
\hline 
\emph{Error string}&
\emph{Reason/description}\tabularnewline
\hline 
Internal error&
Error in internal algorithm\tabularnewline
\hline 
Internal error: can't read local file&
Error manipulating files in the control directory\tabularnewline
\hline 
Failed reading local job information&
-//-\tabularnewline
\hline 
Failed reading status of the job&
-//-\tabularnewline
\hline 
Failed writing job status&
-//-\tabularnewline
\hline 
Failed during processing failure&
-//-\tabularnewline
\hline 
Serious troubles (problems during processing problems)&
-//-\tabularnewline
\hline 
Failed initiating job submission to LRMS&
Could not run backend executable to pass job to LRMS\tabularnewline
\hline 
Job submission to LRMS failed&
Backend executable supposed to pass job to LRMs returned non-zero
exit code\tabularnewline
\hline 
Failed extracting LRMS ID due to some internal error&
Output of Backend executable supposed to contain local ID of passed
job could not be parsed\tabularnewline
\hline 
Failed in files upload (post-processing)&
Failed to upload some or all output files\tabularnewline
\hline 
Failed in files upload due to expired credentials - try to renew&
Failed to upload some or all output files most probably due to expired
credentials (proxy certificate)\tabularnewline
\hline 
Failed to run uploader (post-processing)&
Could not run \emph{uploader} executable\tabularnewline
\hline 
uploader failed (postprocessing)&
Generic error related to \emph{uploader} component\tabularnewline
\hline 
Failed in files download (pre-processing)&
Failed to upload some or all input files\tabularnewline
\hline 
Failed in files download due to expired credentials - try to renew&
Failed to download some or all input files most probably due to expired
credentials (proxy certificate)\tabularnewline
\hline 
Failed to run downloader (pre-processing)&
Could not run \emph{downloader} executable\tabularnewline
\hline
downloader failed (preprocessing)&
Generic error related to \emph{downloader} component\tabularnewline
\hline
User requested to cancel the job&
A-REX detected external request to cancel this job, most probably
issued by user\tabularnewline
\hline
Could not process RSL&
Job description could not be processed to syntax errors or missing
elements\tabularnewline
\hline
User requested dryrun. Job skiped.&
Job description contains request not to process this job\tabularnewline
\hline
LRMS error: (CODE) DESCRIPTION&
LRMS returned error. CODE is replaced with numeric code of LRMS, and
DESCRIPTION with textual description\tabularnewline
\hline
Plugin at state STATE failed: OUTPUT&
External plugin specified in A-REX configuration returned non-zero
exit code. STATE is replcaced by name of state to which job was going
to be passed, OUTPUT by textual output generated by plugin.\tabularnewline
\hline
Failed running plugin at state STATE&
External plugin specified in A-REX configuration could not be executed.\tabularnewline
\hline
\end{tabular}
